---
title: "Statistical Inference - Course Project Part 1"
author: "Michael Celeste"
date: "Saturday, November 22, 2014"
output: html_document
---

The following analysis simulates an exponential distribution where lambda is the rate parameter. The
theoretical mean of the distribution is 1/lambda as well as the standard deviation.

```{r, echo=TRUE}

## Create exponential distribution of averages simulate - 1000
edist <- replicate(1000, mean(rexp(40,0.2)))

## Create a dataframe for ggplot use
df <- data.frame(x=edist)

## Calculate theoretical mean (1/lambda) where lambda = 0.2
mu <- 1/0.2
1/mu^2
## ggplot creation
##gp <- ggplot(df, aes(x=x))
##gp <- gp + geom_histogram(binwidth=0.1, aes(y=..density..), fill="salmon", colour="black")+geom_density()
##gp <- gp + geom_vline(xintercept = mu1, colour="red", size=1)
##gp <- gp + geom_vline(xintercept = mu, colour="green", size=1)

## Standard deviation
sqrt((sum(edist^2) - mean(edist^2))/1000)

```

Theoretical center of the exponential distribut is equal to 1/lambda which is equal to `r mu ` where lambda is equal to 0.2.

The 
Theoretical variance is 1/lambda^2

```{r, echo=FALSE}

hist(edist, breaks=100)

abline(v=mean(edist), col="blue")

abline(v=(1/0.2), col="red")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Use a line graph with colored areas to compare distributions

distribution of sample variances?

